### 2023-09-21 main.tex
fix

In Section \ref{sectionIntegrabiliy}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations. To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal. These boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}. For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.

@@

As a consequence, we can find all the eigenvectors of $H$ from the ones of $H_{0}$. Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM). 

@@

	R(z,H^{''}):=\left(z-H^{''}\right)^{-1}
where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the resolvent is well defined. 

@@

	(z-H^{''})R(H^{''},z)=I

@@

	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1

@@

	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory (see \cite{frassek2020duality}). Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system. This expression allows a simpler treatment of the mapping and allows also to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$. To write formula \eqref{W-extended} through the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}). In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$. 

@@

We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$

@@

	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)

@@

where each of the above element acts on the quantum space $V$. These element satisfy some \textit{exchange relations} that can be found by \eqref{RURU} and they are given by: 

@@

		\sum_{k=0}^{2L+2}Q_{k}x^{k}
where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 

@@

Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ as 

@@

 In the following we will need the charge expansion of $T(x)$. As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed. Therefore, using \eqref{RURU}, we compute: 

@@

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three charges

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
\end{align}
\begin{align}
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
\end{align}
\begin{align}
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
By construction it follows that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}

We also introduce 
\begin{equation}\label{Q-nonDiag}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where, for the sake of notation we denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

@@

We denote its eigenvalues by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$. As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$. On these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

where we denote by 

@@

Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 

@@

	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-\mathcal{Q}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

Equation \eqref{Nice-W2} gives an explicit formula in term of the matrices $B_{1}^{2L-1}$ of the matrix $W$. We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges. We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a different technique to obtain it. 

@@

where in the last equality we used 
	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}

@@

		=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}

@@

Following the result in the simpler $gl(2)$ case, we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$. Using also the multi-variate version of \eqref{veryUsefulSeries}, we obtain
		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)

@@

		\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle

@@

%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

We recall the following notation, already used in \eqref{Tau-Notation}:

@@

We prove the following:

@@

Using \eqref{BActionVoid} and \eqref{Commutativity-Gained} we have that for all $i,j\in\{1,\ldots,N-1\}$

@@

	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

\subsection{Bethe ansatz solution}
Describe eigenvalues of $T_0$ following 
\cite{belliard2} 

@@

In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$. Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one (i.e. $H_{0}$) as

@@

More explicitly we have 

@@

	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\\&
	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&

@@

The aim of this section is studying some extension to the analysis previously done when integrability property is lost. We fix $\nu>1$ and, for the sake of simplicity, we still study the geometry of chain. We provide the following extensions: 

@@

	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is constructed with the goal of having the average density evolving a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Subsection \ref{Subsection-RD}

@@

As already mentioned, we will redistribute particles on a bond according to a probability measure that is the reversible one \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond. We denote

@@

	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=1}^{N-1}r_{a}

>>>>

In Section \ref{sectionIntegrabiliy}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations. To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal. These diagonal boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}. For this reason, we say that the process is mapped onto equilibrium.

@@

As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$. Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM), to be constructed. 

@@

	\mathcal{R}(z,H^{''}):=\left(z-H^{''}\right)^{-1}
where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the $\mathcal{R}(x,H^{''})$ is well defined. 

@@

	(z-H^{''})\mathcal{R}(H^{''},z)=I

@@

	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1

@@

	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{E}_{\bm{m}}\mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \mathcal{R}(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory (see \cite{frassek2020duality}). Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system. This expression allows a simpler treatment of the mapping and also allows to  find a closed formula for the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$. To achieve this aim, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}). In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$ situation. 

@@

We introduce the \textit{quantum space} $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the \textit{auxiliary space} $V_{0}$. In the case of the multi-species stirring process we chose $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We define the following $R$-matrices acting on the tensor product of spaces with indices $a,b=0,1,\ldots,L$

@@

	U_{0}(x)=M_{0}(x)\widehat{K}_{0}(x)\widehat{M}_{0}(x)

@@

where each of the above element acts on the quantum space $V$. Using \eqref{RURU}, we find some \textit{exchange relations} that the elements of $U_{0}(x)$ must satisfy: 

@@

		\sum_{k=0}^{2L+2}Q^{k}x^{k}
where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q^{k}$ the \textit{conserved charges} of the system. 
We also introduce 

@@

Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ 

@@

We will need the charge expansion of $T(x)$. As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed. Therefore, using \eqref{RURU}, we compute: 

@@

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three conserved charges of the system

\begin{align}
Q^{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
\end{align}
\begin{align}
Q^{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
\end{align}
\begin{align}
Q^{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q^{2L+2}$ and $Q^{2L+1}$ are proportional to the identity matrix, while $Q^{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
By construction it follows that 
\begin{equation}
\left[Q^{2L},H^{''}\right]=Q^{2L}H^{''}-H^{''}Q^{2L}=0
\end{equation}
while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
\begin{equation}
Q^{2L}_{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q^{2L}_{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}

We also introduce 
\begin{equation}\label{Q-nonDiag}
Q_{+}^{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where, for the sake of notation we denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we can write 
\begin{equation}
Q^{2L}=Q^{2L}_{0}+Q_{+}^{2L}
\end{equation}
Observe that $Q^{2L}$ and $Q^{2L}_{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

@@

Moreover, we denote its eigenvalues by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$. As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$. On these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

In the following, we will denote by 

@@

Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q_{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 

@@

	W&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\;|\bm{m}|=1}\left(\Lambda_{\bm{m}}+\epsilon-Q^{2L}_{0}-Q_{+}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

Equation \eqref{Nice-W2} gives an explicit formula in term of the matrices $B_{1}^{2L-1}$ of the matrix $W$. We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges. We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a slightly different technique to obtain it. 

@@

where in the last equality we used that $\forall m\in \{1,\ldots,L\}$
	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}\rangle=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}|\Psi_{m}\rangle

@@

		=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}

@@

Performing a multi-variable power expansion of formula \eqref{WInCharges} with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)

@@

		\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle

@@

%		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilonQ_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilonQ_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

We recall the notation, already used in \eqref{Tau-Notation}:

@@

We prove that:

@@

For all $i,j\in\{1,\ldots,N-1\}$

@@

	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

%\subsection{Bethe ansatz solution}
%Describe eigenvalues of $T_0$ following 
%\cite{belliard2} 

@@

In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$

@@

 Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one $H_{0}$ as 

@@

	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\nonumber\\&
	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\nonumber\\&

@@

The aim of this section is studying some extension of the analysis previously done when integrability property is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 

@@

	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is carefully constructed with the goal of having the average density evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Duality for the boundary driven process is proved. Subsection \ref{Subsection-RD}

@@

We introduce the reversible measure \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond

@@

	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{N}=\nu-\sum_{a=1}^{N-1}r_{a}
 Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
